% request for removal from telemarketing lists

\documentclass[10pt]{letter}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in


\name{	Joshua T.\ Vogelstein \\ 
		Johns Hopkins University \\
		Ph.D.\ Candidate in the Dept.\ of Neuro. \\
		% Postdoc.\ at Nat'l Center of Applied Neuro. \\
		% and the Department of Applied Mathematics and Statistics \\
		3400 N.\ Charles St.\ \\
		Krieger Hall, Rm.\ 338 \\
		Baltimore, MD 21205 \\
      	(443) 858-9911}

\date{\today}

\begin{document}


\begin{letter}{	Prof.\ Gerald Edelman, M.D.\, Ph.D.\ \\
               	Chairman,The Scripps Research Institute \\
				10550 N.\ Torrey Pines Rd.\ \\
               	La Jolla, CA  92037-1000}   
                           
\opening{Dear Professor Edelman:}

On behalf of myself and my coauthors, I submit for your review a copy of our
manuscript entitled, ``Are mental properties supervenient on brain properties?''
We hope that you will consider ``communicating'' this manuscript to the
prestigious Proceedings of the National Academy of Sciences (PNAS).  

At the core of this paper is a thought experiment in which we mathematically
prove that if the graph corresponding to brain connectivity (i.e., the
\emph{connectome}) is statistically related to a particular mental property
(e.g., propensity for mathematics), one could build a classifier to determine
whether any individual's brain exhibits that property with an arbitrarily small
misclassification rate.  The proof follows directly from the probabilistic
theory of pattern recognition and is made possible by our novel exposition of
universal consistency for a $k_n$-nearest neighbor classifer on graphs.  In
addition to these theoretical results, the manuscript describes a simulation
that suggests how one could actually build such a classifier for the ``brain''
of \emph{Caenorhabditis elegans} using today's technology.

Our results have many implications, some philosophical, some statistical, and
some pragmatic.  First, the philosophical implications:  The relationship
between the mind and brain has been investigated for millennia, using tools
ranging from abstract arguments to microstimulation of individual neurons.
However, until now, no one (to our knowledge) has proposed a framework that
allows for empirical investigation of this relationship at the scale of the
connectome.  Such a framework will undoubtedly be of value as the multiple
ongoing large-scale efforts to collect a connectome (cf.\ NIH Human Connectome
Project) begin paying dividends. 

%Rather, it seems the typical approach is to first \emph{assume} such
%a relationship exists, and then find the \emph{location} of that relationship
%(to make a crude analogy, much of contemporary neuroscience seems to have taken
%a lesson from Decartes, who, assuming a relationship between an immaterial soul,
%and the body, found that the pineal gland was the location).  

In addition to the philosophical implications, our work has significant
statistical implications.  Whereas several groups have recently proposed
algorithms for classifying graphs, there exists very little theoretical work on
the limitations of these tools.  In contrast, our work is founded on an
existance proof of a universally consistent classifier on graphs, the
limitations of which are both known and well-understood.  Although we only apply
this classifier to simulated brain-derived graphs, the methods are applicable to
many other kinds of graphical data. The recent emergence of networks and graphs 
as the preferred representations of structured relationships in multiple
scientific disciplines suggests that the development of statistical tools for
rigorous analysis of network data is a pressing need for the scientific
community at large.  
%Furthermore, we show using the arbitrarily slow convergence
%theorems, that only a one-sided result is possible, i.e., while we can be
%$100(1-\alpha)\%$ confident of the relationship between the properties under
%investigation, we can \emph{never} be confident in its negation.  This result
%is widely applicable outside the investigation of mind-brain supervenience.

Finally, the results described in this manuscript have pragmatic implications.
Studies relating brain structure to brain function are being published with
increasing frequency due to the increasing availability of diffusion-weighted
magnetic resonance imaging and other connectivity-imaging technologies.  However,
without sophisticated statistical tools for the analysis of such data, to-date
the findings have (mostly) been limited to linear correlations between scalar
measures of connectivity and the brain function under investigation.  The
graph-theoretic approach proposed here allows for utilizing the entirety of the
information obtained from such measures, rather than using simple descriptive
statistics.

In summary, we believe that the work described in this manuscript makes
significant contributions in several contemporary fields of inquiry, and is
therefore suited for a general-audience peer-reviewed journal such as PNAS.  Your
interest in the philosophical underpinnings of neuroscience, as well as in
inferring causal relationships from neural data and generating large-scale
simulations of neural populations suggests to us that this manuscript would of
interest to you.  Please do not hesitate to contact us with any questions or
comments.

\closing{Respectfully,}



\end{letter}


\end{document}
